Investigating Interventions

### 2023-03-01 minos/validation/interventions.Rmd
Added a subtitle to each pathway plot to show which intervention it is showing

```{r}
compare_housing_out(base, energy)
```

### Neighbourhood Safety

```{r}
compare_neighbourhood_out(base, energy)
```

### Tobacco Use

```{r}
compare_ncigs_out(base, energy)
```

### Nutrition Quality

```{r}
compare_nutrition_out(base, energy)
```

### Loneliness (NOT CURRENTLY IN SF12 MODEL)

```{r}
compare_loneliness_out(base, energy)
```

@@

```{r}
compare_housing_out(base, wage)
compare_neighbourhood_out(base, wage)
compare_ncigs_out(base, wage)
compare_nutrition_out(base, wage)
compare_loneliness_out(base, wage)
```

@@

```{r}
compare_housing_out(base, allchild)
compare_neighbourhood_out(base, allchild)
compare_ncigs_out(base, allchild)
compare_nutrition_out(base, allchild)
compare_loneliness_out(base, allchild)
```

>>>>

```{r}
int.name <- 'Energy'
compare_housing_out(base, energy, int.name)
compare_neighbourhood_out(base, energy, int.name)
compare_ncigs_out(base, energy, int.name)
compare_nutrition_out(base, energy, int.name)
compare_loneliness_out(base, energy, int.name)
```

@@

```{r}
int.name <- 'Living Wage'
compare_housing_out(base, wage, int.name)
compare_neighbourhood_out(base, wage, int.name)
compare_ncigs_out(base, wage, int.name)
compare_nutrition_out(base, wage, int.name)
compare_loneliness_out(base, wage, int.name)
```

@@

```{r}
int.name <- 'All Child'
compare_housing_out(base, allchild, int.name)
compare_neighbourhood_out(base, allchild, int.name)
compare_ncigs_out(base, allchild, int.name)
compare_nutrition_out(base, allchild, int.name)
compare_loneliness_out(base, allchild, int.name)
```
